% Conclusion

We document that the securities lending market serves as an information acquisition channel for active mutual fund managers. Using unique regulatory data from the Deutsche Bundesbank with security-level lending positions, we show that active fund managers reduce their holdings in stocks they lend. The effect is economically large---a 0.33 percentage point position reduction per one-standard-deviation increase in lending activity---and is absent for passive funds, who cannot adjust their portfolios in response to the signal.

We identify the mechanism through mandatory short position disclosure events under EU regulation. Active funds reduce positions substantially more when lending precedes a disclosure event, confirming that the information content of lending drives the trading response. The timing is consistent with anticipation: only the lead disclosure amplifies the effect, while contemporaneous and lagged disclosures are uninformative. Results are robust to using passive fund lending as an exogenous source of variation in lending activity.

We further show that information flows within fund families, with the strongest effects from same-manager fund lending. The trading response is amplified in concentrated lending markets where individual transactions carry more informational weight.

Our findings contribute to the understanding of how information flows through financial markets. The securities lending market, typically studied from the perspective of short sellers, also functions as an information channel for the long side of the market. Fund managers who participate in lending gain private, real-time information about short-selling demand that enables them to make more informed portfolio decisions.

These results have implications for the welfare distribution in financial markets. Active fund managers who lend benefit from an informational advantage that allows them to reduce positions before adverse price movements materialize, generating gains for their investors at the expense of uninformed buyers on the other side of the trade. Short sellers, in turn, may face higher borrowing costs or reduced lending supply if lenders anticipate acting on the information, consistent with the commitment problem modeled by \citet{Nurisso2026} and the evidence in \citet{PaliaSokolinski2024} that short sellers prefer passive lenders precisely because they cannot exploit the signal. Market concentration amplifies these information asymmetries: in thin lending markets, the information advantage accrues to a small number of participating families, with distributional consequences for price efficiency.

Our study examines the period December 2014--December 2018, prior to the implementation of the Securities Financing Transactions Regulation (SFTR), which took effect in 2020 and introduced transaction-level reporting requirements for securities lending. SFTR materially increases the transparency of the lending market and may attenuate the private information advantage we document. Whether the lending-information channel survives under SFTR's enhanced disclosure regime is an important question for future research.

These results have broader implications for the regulation of securities lending, the organization of fund families, and the design of mandatory disclosure regimes. Our evidence suggests that lending market structure---particularly the degree of concentration---is a first-order determinant of how much private information flows to active managers, with implications for policymakers considering reforms to lending market infrastructure.
