% Institutional Background and Data

\subsection{German Securities Lending Regulation and Comparison with the United States}

The German securities lending framework and the U.S.\ framework share the same statutory core. In the United States, securities lending by registered investment companies is governed by guidance under the Investment Company Act of 1940 and informal SEC guidance (Division of Investment Management Guidance Update No.\ 2014-06), requiring full collateralization of loans, conservative collateral reinvestment, and preserved recall rights; U.S.\ funds may lend at most one-third of total assets \citep{Honkanen2025}. In Germany, Sections 200 to 202 of the \textit{Kapitalanlagegesetzbuch} (KAGB) impose closely analogous requirements: (i) lending transactions with any single counterparty must not exceed 10\% of a fund's net asset value; (ii) funds must receive collateral worth at least 100\% of the loan value; (iii) collateral must be held in high-quality sovereign debt, short-term money market funds, or repurchase agreements; (iv) remuneration must reflect current market conditions; and (v) funds must be able to terminate any loan at any time. Both systems therefore guarantee that lending is fully collateralized and callable on demand, making loan recall feasible regardless of short-selling pressure.

The two markets differ in two economically relevant respects. First, European UCITS rules require that 100\% of net lending revenue --- after operational costs --- be returned to the lending fund, while U.S.\ fund boards have discretion over the revenue split between the fund and its lending agent. In practice, German and European funds receive between approximately 50\% and 95\% of gross revenue \citep{voicu_prache:2019}, while U.S.\ splits typically run 60\%--80\% fund / 20\%--40\% agent \citep{EvansFerreiraPrado2017}. Second, the dominant collateral type differs: cash collateral accounts for roughly 80\% of U.S.\ securities loans, while non-cash collateral (primarily sovereign debt) accounts for approximately 60\% of European loans \citep[Financial Stability Board]{jank_smajlbegovic:2015}. These differences affect the economics of lending but not its information content.

The most consequential institutional difference for the information channel we study is the lending-agent structure. In the United States, most securities lending is intermediated by third-party custodian banks --- subsidiaries of State Street, BNY Mellon, and JPMorgan --- that manage lending programs for multiple unrelated fund families and do not disclose borrower identity to the fund manager \citep{baklanova_caglio_keane_porter:16}. In Germany, by contrast, larger fund families typically operate in-house lending desks --- organizational units within the fund management company (\textit{Kapitalverwaltungsgesellschaft}, KVG) --- that pool lending across funds in the family and negotiate directly with prime broker counterparties. This in-house structure creates organizational proximity between the entity observing borrowing demand and the portfolio managers who make trading decisions. The identity of the short-seller counterparty, the size of the loan, and the terms of the borrowing arrangement are visible within the same organizational entity that manages the portfolio. \citet{Honkanen2025} documents that U.S.\ active mutual funds also reduce positions in lent stocks, suggesting that even third-party intermediation does not fully eliminate information transmission; but the transmission channel is more direct in the German in-house model, which is consistent with our finding that the information effect is strongest through same-manager lending.

The most important regulatory difference for identification is the short-position disclosure regime. In the United States, FINRA publishes biweekly aggregate short interest reports by security, with no identification of individual short sellers regardless of position size, and with a publication lag of approximately one to two weeks. In the European Union, Regulation (EU) No.\ 236/2012 requires any investor whose net short position exceeds 0.5\% of a company's issued share capital to publicly disclose the position --- including the investor's identity, position size, and relevant issuer --- to the national competent authority (BaFin in Germany) by the next business day. This creates a uniquely granular, near-real-time record of large short-seller positions with no direct U.S.\ analogue. Positions above 0.2\% trigger a private notification to BaFin but are not publicly disclosed; positions above 0.5\% are posted publicly on the BaFin website. \citet{jank_roling_smajlbegovic2020} document that short sellers strategically pile up positions just below the 0.2\% private notification threshold, with an estimated excess mass of 92.8\% below that threshold for first-time disclosers, consistent with informed short sellers placing significant value on maintaining the secrecy of their positions before disclosure.

This disclosure architecture is the foundation of our identification strategy. Before a short position crosses the 0.5\% public disclosure threshold, the private information that a large short seller is accumulating a position exists only in the lending book of the fund lending the shares. The moment that position becomes public, the information transitions from private to common knowledge: \citet{jones_reed_waller:16} show that public disclosures under Regulation 236/2012 reduce short interest and bid-ask spreads, confirming that the disclosure event is informative. The EU regime thus creates a precisely datable stock-level information event --- the transition from private to public knowledge --- that allows us to test whether active fund managers who observe borrowing demand through lending trade in anticipation of the disclosure. Because U.S.\ short interest reporting is aggregate, anonymous, and biweekly, no equivalent scheduled information transition exists in the U.S.\ context. The German regulatory environment is therefore uniquely suited to our identification strategy, while the core mechanism --- funds acting on private information from lending activity --- is broad enough to generalize, as documented by \citet{Honkanen2025} in U.S.\ data and consistent with the strategic borrowing equilibrium studied by \citet{PaliaSokolinski2024}, in which short sellers prefer lending from passive investors precisely because such funds do not extract and act on the lending signal.

\subsection{Data Sources}

Our data on German mutual funds comes from the Investment Funds Statistics (IFS) of the Deutsche Bundesbank, covering December 2014 through December 2018. Since September 2009, all investment companies domiciled in Germany must report general fund information and portfolio holdings to the IFS. The data are collected monthly and provide detailed end-of-month, security-by-security information about each fund's portfolio. For each holding, a fund reports the ISIN, the number of shares held, and the nominal and market value of the position.\footnote{\citet{doetsch_flory_schoenberg:2018} provide a detailed description of the IFS data.}

In December 2014, the Bundesbank introduced a major reporting change requiring funds to disclose securities lending activities. For each security in the portfolio, each fund must report the end-of-month nominal value of any position held in a lending transaction.\footnote{Securities lending information is reported at the fund-security level and is therefore constant across all share classes of an individual fund.} This regulatory change provides us with a unique dataset: security-level lending positions for the universe of German investment funds.

We merge the IFS data with Morningstar fund information and aggregate the data to the fund level, matching share class ISINs to the fund identifier provided by Morningstar. For funds with multiple share classes, we calculate fund returns and expenses as asset-weighted averages across share classes. For assets under management, fund flows, and fund holdings, we aggregate across all share classes. Fund age is based on the inception date of the oldest share class.

We combine the IFS mutual fund data with stock information from Datastream, securities lending data from IHS Markit, and the Fama-French risk factors from Kenneth French's data library.\footnote{Following \citet{Ferreira_etal2018JF}, we estimate four-factor alphas using regional factors based on a fund's investment region and use world factors for global funds.}

\subsection{Sample Construction}

The initial IFS-Morningstar matched sample consists of 2,044 funds from 58 fund families. We apply several filters. First, we exclude closed-end funds and alternative investment funds. Second, we remove non-equity, sector, and emerging market funds based on their Morningstar category. Third, we keep only funds older than three years with more than \$10 million in assets under management to mitigate potential incubation biases \citep{evans:2010}. Our final sample consists of 320 German open-end equity mutual funds from 36 fund families.

We further restrict our sample to holdings of securities identified as common or preferred equity, excluding approximately 2\% of observations. We retain only securities traded in the 23 developed markets listed in \citet{fama_french:2012}, excluding another 2\% of observations. We drop observations where the reporting date of the holding in the IFS data exceeds the stock's delisting date in Datastream (less than 0.5\% of observations) and remove fund-month pairs where a fund closes all positions, as we assume the fund is liquidated (less than 0.5\% of observations).

\subsection{Variable Construction}

We use the Bundesbank holdings data to construct two variables capturing the monthly trading activity of a fund. $PosChange_{i,j,t}$ is the percentage change in the number of shares of stock $i$ held by fund $j$ in month $t$, adjusted for stock splits and winsorized at the 99.5\% level. For securities lending activity, we compute $sh\_sec\_lend_{i,j,t}$, defined as the fraction of a particular portfolio position in stock $i$ lent by fund $j$ in month $t$.

At the stock level, we measure aggregate shorting demand as the value of securities on loan scaled by the total market capitalization of that security ($OnLoan$), obtained from IHS Markit.

\subsection{Descriptive Statistics}

Table~\ref{table_desc_stats_investment} presents the breakdown of our sample by investment focus. Of the 320 funds, 267 are actively managed and 53 are passively managed. In terms of investment focus, 92 funds have a global focus, 135 focus on European equities, and 58 focus on German equity, with total assets under management of EUR~156.75 billion.

Table~\ref{table_desc_stats_seclending} provides summary statistics on the securities lending behavior of German investment funds. A third of all funds participate in securities lending during our sample period. The share of securities lenders is considerably lower for actively managed funds (25.47\%) compared to passive funds (69.81\%). Investment funds typically lend only a small fraction of their portfolio, with an average of 3.8\% of AUM on loan. These figures are comparable to U.S.\ mutual fund lending practices documented in \citet{prado_saffi_sturgess:14} and the Investment Company Institute \citep{ICI2014Viewpoints}.

Table~\ref{table_desc_stats} presents descriptive statistics for the monthly fund-security panel data. Panel~A focuses on portfolio characteristics. Portfolios are well-diversified, with a mean (median) portfolio holding of 1.1\% (0.63\%). On average, 2\% of a fund's positions are lent in a given month and 5\% over the past twelve months. The relative frequency with which funds exit a position is 4\%.

Panel~B presents stock-level characteristics. For stocks held by German investment funds, total shorting demand ($OnLoan$) has a mean of 2.52\% and a median of 0.38\% of market capitalization. Average lending supply is 17.89\% and the mean short fee is 75.98 basis points per annum, reflecting the presence of some high-fee ``specials.''

Panels~C and~D report fund-level and fund family-level characteristics, respectively. In our sample, 85\% of observations come from active funds and 15\% from passive funds. Overall, 20\% of observations are from funds that participated in the securities lending market in a given month. At the family level, 17\% of observations come from families with at least one fund participating in lending.
