% Information Acquisition Channel

The baseline results establish that active funds reduce positions in stocks they lend. We now investigate the mechanism: do funds trade on information acquired through the lending process? The model in \citet{Nurisso2026} provides a precise prediction: lenders observe that a short seller is willing to borrow, which is informative about the stock's future value. This private signal is valuable precisely \emph{before} the short seller's position crosses the mandatory public disclosure threshold. Once disclosed, the information is public and the lender's informational advantage evaporates. We exploit mandatory short position disclosure events---as described in Section~\ref{subsec:identification-disclosure}---as an external validation of this mechanism. The key identification test is whether active lenders reduce positions specifically in the month \textit{before} a large short position is publicly disclosed, consistent with exploiting private information embedded in the lending contract that is not yet visible to the market.

\subsection{Mandatory Short Position Disclosure}

Table~\ref{table_disclosure} presents the results, estimated on the disclosure sample (observations within $\pm 3$ months of a first-time large short position disclosure for stocks that are ever publicly disclosed). The dependent variable is $PosChange_{i,j,t}$. $OnLoan_{i,j,t-1}$ is standardized lending activity; $\mathit{Disclosure}_{i,t+1}$ equals one if stock $i$ has a \textit{new} public short position disclosure in month $t+1$ (defined as having no prior disclosure in the preceding six months). All specifications use active funds and double-cluster standard errors by fund and time.

Column~(1) reports the baseline lending effect for this restricted sample: $OnLoan_{i,j,t-1} = -0.2837$, $t = -2.85$, confirming the baseline result holds in the disclosure sample. Column~(2) adds the disclosure indicator, which is positive but insignificant ($0.3633$, $t = 1.25$), consistent with an absence of general reaction to impending disclosures among both lenders and non-lenders alike (this effect is absorbed by the stock$\times$time fixed effects in the saturated specification).

Column~(3) introduces the key interaction: $OnLoan_{i,j,t-1} \times \mathit{Disclosure}_{i,t+1}$. The interaction coefficient is $-0.8027$ and statistically significant at the 5\% level ($t = -2.68$). Active funds reduce their positions substantially more---by an additional 0.80 percentage points per standard deviation of lending---when their lending activity precedes a new disclosure event by one month. Column~(4) adds the full saturated three-way fixed effects; the interaction coefficient strengthens to $-0.8622$ ($t = -2.22$), allaying concerns that the result is driven by unobserved stock-time or fund-time factors.

Columns~(5)--(7) replicate columns~(1)--(3) using a lower-dimensional fixed effects structure (separate security, fund, and time fixed effects rather than their pairwise interactions); the results are qualitatively identical, confirming robustness to the fixed effects specification.

Column~(8) provides the critical placebo test. Estimating the identical specification for passive funds only, the coefficient on $OnLoan_{i,j,t-1}$ is economically small and insignificant ($0.0208$, $t = 0.23$), and the interaction with $\mathit{Disclosure}_{i,t+1}$ is precisely zero ($0.0258$, $t = 0.28$). Passive funds show no trading reaction to lending signals around disclosure events. This placebo result strongly supports the information acquisition interpretation: only funds with discretion to trade on private information do so.

\subsection{Reduced-Form Robustness: Passive Fund Lending}

A potential concern is that a fund's own lending activity is endogenous to its trading decisions---a fund might selectively reduce positions in stocks it plans to stop lending, creating a spurious negative correlation. As a reduced-form robustness check, we replace $OnLoan_{i,j,t-1}$ with $\mathit{OnLoan}_{i,f\text{-passive},t-1}$, the aggregate lending of stock $i$ by passive funds in the same family (Table~\ref{table_passive_rf}). Since passive funds track indices and cannot adjust portfolio weights discretionarily, their lending is governed by portfolio composition and borrower demand rather than by active rebalancing decisions. This substitution provides a robustness check because the passive lender's decision to lend a given stock is plausibly unrelated to the active manager's concurrent trading plans.\footnote{This specification is a reduced-form regression, not a two-stage instrumental variables estimator. We do not report a first stage here because doing so requires a maintained exclusion restriction that passive fund lending affects active fund trading \emph{only} through within-family information transmission---a restriction that is economically plausible but is not directly testable. Potential violations include correlated borrower demand (a short seller approaching family $f$ simultaneously negotiates with both passive and active funds in the family) and common benchmark overweights (both fund types hold concentrated positions in stock $i$ due to shared index exposure). The results below should be interpreted as consistent with the information channel story, not as a causal identification of it. We plan to implement a formal IV design with a reported first stage and instrument diagnostics in the revision.}

The coefficient on passive fund lending is $-0.3406$ ($t = -3.20$) in column~(1), comparable to the baseline. The interaction with $\mathit{Disclosure}_{i,t+1}$ in column~(3) is $-1.1240$ and significant at the 1\% level ($t = -3.29$)---larger in magnitude than the baseline interaction ($-0.8027$). The larger magnitude is consistent with passive fund lending providing a signal that is less contaminated by the active manager's own rebalancing decisions, though part of the difference could also reflect measurement-error attenuation in the fund-level measure that is reduced by family aggregation. Column~(4) confirms robustness with saturated fixed effects ($-0.9156$, $t = -2.32$). These results are consistent with the trading response being robust to this alternative lending measure, though they do not fully resolve the endogeneity concern in the absence of a formal IV structure.

\subsection{Timing Tests: Leads and Lags of Disclosure}

If active funds genuinely acquire information through lending and trade in anticipation of future short-selling pressure, only the \textit{lead} disclosure should predict trading. Contemporaneous and lagged disclosure interactions should be small once the information has become public.

Table~\ref{table_timing} tests this prediction by including interactions of $OnLoan_{i,j,t-1}$ with $\mathit{Disclosure}_{i,t+1}$ (lead), $\mathit{Disclosure}_{i,t}$ (contemporaneous), and $\mathit{Disclosure}_{i,t-1}$ (lag). Column~(3) shows that only the lead interaction is statistically significant ($-0.8224$, $t = -2.62$). The contemporaneous interaction is economically negligible ($0.0353$, $t = 0.08$) and the lagged interaction is small and insignificant ($-0.1157$, $t = -0.62$). Column~(4) with saturated fixed effects confirms this pattern: the lead interaction is $-0.8723$ ($t = -2.27$), while contemporaneous and lagged interactions remain insignificant.

This timing pattern---pre-announcement selling by lenders but not in response to past or contemporaneous disclosure---is precisely what the information acquisition channel predicts. Active lending funds reduce positions in the month before a large short position becomes publicly known, consistent with observing borrowing demand before it crosses the public disclosure threshold.

Two interpretive notes are warranted. First, the $\pm 3$-month sample window means that $\mathit{Disclosure}_{i,t-1} = 1$ is observed in months when the large short position is already public information; in these months, any information advantage from lending has evaporated and position changes naturally revert toward zero, mechanically dampening the lagged interaction coefficient. The asymmetry test is therefore most credibly interpreted as showing that the lead interaction is significantly negative while the other interactions are near zero, rather than claiming the three coefficients are statistically different from each other. Formal Wald tests of $H_0\colon \beta_{\text{lead}} = \beta_{\text{lag}}$ and sensitivity analysis across alternative window widths are deferred to the revision. Second, the magnitude of the lagged interaction in column~(4) is $-0.3043$ ($t = -1.34$), which is economically non-negligible and one-sided borderline significant; while it does not meet conventional significance thresholds, it is inconsistent with a clean zero and merits a formal test in the revision.
