% Market Structure and Information Acquisition

We next examine whether the informativeness of the lending signal varies with the structure of the lending market. If lending conveys private information about short-selling demand, the signal should be more informative when lending is concentrated---each individual lending transaction is then more likely to reflect informed, sizeable short selling activity.

We aggregate lending to the fund-family level for this analysis, using $OnLoan_{i,f,t-1}$---the total dollar value of stock $i$ lent by all funds in family $f$ at month $t-1$ divided by market capitalization, standardized to mean zero and unit variance. There are two reasons for this aggregation. First, market structure variation operates at the family level: the number of active lending agents, the HHI of lending concentration, and family portfolio breadth are inherently family-level constructs that capture the organizational unit through which lending decisions and information flow. Second, and more importantly, the concentration mechanisms we test---fewer counterparty relationships and more concentrated portfolios---generate more precise signals precisely because the family observes a larger share of total borrowing demand for a given stock. Fund-level lending would mechanically understate the information set available to a fund manager whose family coordinates lending through a centralized desk. In unreported robustness tests, the qualitative results hold when using fund-level lending instead, but are weaker in magnitude, consistent with family aggregation capturing the relevant information unit.

We test this by interacting family-level lending ($OnLoan_{i,f,t-1}$) with measures of lending market concentration and with the mandatory disclosure indicator.

Table~\ref{table_market_structure} presents the results, all estimated with the full saturated fixed effects (security$\times$time, fund$\times$time, fund$\times$security), active funds only, and standard errors double-clustered by fund and time. Column~(1) reproduces the baseline: $OnLoan_{i,f,t-1} = -0.4226^{**}$ ($t = -2.35$) with a disclosure interaction of $-0.8633^{**}$ ($t = -2.32$). The key variable throughout is \textit{family-level} lending, $OnLoan_{i,f,t-1}$, measured as the aggregate dollar value of stock $i$ lent by all funds in family $f$ divided by market capitalization, standardized to mean zero and unit variance.

We consider five standardized measures of concentration. At the stock level: the Herfindahl--Hirschman index of lending concentration across families ($\mathit{HHI}^{\mathit{stock}}_{i,t-1}$, columns~2--3) and the inverse of the number of active lending agents ($1/\mathit{ActiveAgents}_{i,t-1}$, columns~4--5). At the family level: the family's own lending portfolio concentration ($\mathit{HHI}^{\mathit{family}}_{f,t-1}$, columns~6--7), the inverse of the number of stocks held ($1/\mathit{StocksHeld}_{f,t-1}$, columns~8--9), and the inverse of the number of stocks lent ($1/\mathit{StocksLent}_{f,t-1}$, columns~10--11). For each concentration measure, we show a specification with only the pairwise interaction ($OnLoan \times \mathit{Concentration}$, even columns) and one adding the triple interaction with disclosure ($OnLoan \times \mathit{Concentration} \times \mathit{Disclosure}_{i,t+1}$, odd columns).

The results support the information concentration hypothesis. At the stock level, fewer active lending agents amplifies the signal: the triple interaction $OnLoan_{i,f,t-1} \times 1/\mathit{ActiveAgents} \times \mathit{Disclosure}_{i,t+1}$ is $-9.2142^{**}$ ($t = -2.41$, column~5). When fewer agents intermediate the lending market for a stock, the private signal observed by each participating lender is correspondingly more informative about the specific identity and size of the short position being built.

Family-level concentration further amplifies the effect. The triple interaction with family HHI is $-3.0048^{*}$ ($t = -1.94$, column~7): families that concentrate their lending in fewer stocks hold more concentrated positions in each borrower relationship, making each lending contract more informative. The strongest result comes from the inverse of stocks lent: $OnLoan \times 1/\mathit{StocksLent} \times \mathit{Disclosure}_{i,t+1} = -8.1425^{***}$ ($t = -3.96$, column~11). When a family lends fewer distinct securities, each lending relationship provides a larger information share about short selling activity in that stock.

These heterogeneity results reinforce the information acquisition interpretation. The trading response to lending signals is amplified precisely where information concentration is highest---a pattern that is difficult to reconcile with mechanical alternatives and is instead consistent with fund managers extracting and acting on informative signals embedded in the borrowing demand observed through their lending operations. The findings also have implications for market design: policy interventions that fragment the lending market (reducing concentration) may diminish the informational efficiency gains that lending currently provides to active fund managers.
