{\small
\begin{tabular}{l*{4}{c}}
\toprule
 & (1) & (2) & (3) & (4) \\
\midrule
$\mathit{OnLoan}_{i,f\text{-passive},t-1}$ & $-$0.3406$^{***}$ & $-$0.3399$^{***}$ & $-$0.2005$^{*}$ & $-$0.4475$^{**}$ \\
 & ($-$3.20) & ($-$3.18) & ($-$1.78) & ($-$2.35) \\[0.3em]
$\mathit{Disclosure}_{i,t+1}$ & & 0.3600 & 0.3304 & \\
 & & (1.25) & (1.16) & \\[0.3em]
$\mathit{OnLoan}_{i,f\text{-passive},t-1} \times \mathit{Disclosure}_{i,t+1}$ & & & $-$1.1240$^{***}$ & $-$0.9156$^{**}$ \\
 & & & ($-$3.29) & ($-$2.32) \\
\midrule
Controls & Yes & Yes & Yes & Yes \\
\midrule
Security FE & Yes & Yes & Yes & \\
Fund FE & Yes & Yes & Yes & \\
Time FE & Yes & Yes & Yes & \\
Security $\times$ Time FE & & & & Yes \\
Fund $\times$ Time FE & & & & Yes \\
Fund $\times$ Security FE & & & & Yes \\
\midrule
SE Clustering & Fund, Time & Fund, Time & Fund, Time & Fund, Time \\
Sample & Active & Active & Active & Active \\
$N$ & 42,512 & 42,512 & 42,512 & 39,109 \\
\bottomrule
\end{tabular}
}
\par\smallskip
{\footnotesize
\textit{Notes:} The table reports results from panel regressions of $PosChange_{i,j,t}$, the monthly percentage change in fund $j$'s position in stock $i$, using passive fund lending as an exogenous measure of short selling demand. The sample is restricted to actively managed funds in the disclosure sample. $\mathit{OnLoan}_{i,f\text{-passive},t-1}$ is the aggregate dollar value of stock $i$ lent by \textit{passive} funds in family $f$ at month $t-1$, divided by the market capitalization of stock $i$, standardized to mean zero and unit standard deviation. Because passive funds track benchmark indices and cannot trade on information, their lending activity is driven by portfolio composition and borrower demand rather than strategic portfolio decisions, providing an exogenous source of variation in short selling demand signals available to the family. $\mathit{Disclosure}_{i,t+1}$ equals one if stock $i$ has a new mandatory public short position disclosure in month $t+1$ (no prior disclosure in the preceding six months). Controls include lagged Amihud illiquidity rank and lagged position weight. Standard errors are double-clustered by fund and time. \textit{t}-statistics in parentheses. *, **, *** denote significance at the 10\%, 5\%, and 1\% levels.
}
