{\footnotesize
\begin{tabular}{l*{8}{c}}
\toprule
 & \multicolumn{7}{c}{Active Funds} & Passive Funds \\
\cmidrule(lr){2-8} \cmidrule(lr){9-9}
 & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) \\
\midrule
$\mathit{OnLoan}_{i,j,t-1}$ & $-$0.2837$^{***}$ & $-$0.2835$^{***}$ & $-$0.1868 & $-$0.2321 & $-$0.2848$^{***}$ & $-$0.2841$^{***}$ & $-$0.2124 & 0.0208 \\
 & ($-$2.85) & ($-$2.86) & ($-$1.63) & ($-$0.87) & ($-$2.87) & ($-$2.85) & ($-$1.53) & (0.23) \\[0.3em]
$\mathit{Disclosure}_{i,t+1}$ & & 0.3633 & 0.3398 & & & 0.3618 & 0.3391 & \\
 & & (1.25) & (1.17) & & & (1.25) & (1.17) & \\[0.3em]
$\mathit{OnLoan}_{i,j,t-1} \times \mathit{Disclosure}_{i,t+1}$ & & & $-$0.8027$^{**}$ & $-$0.8622$^{**}$ & & & $-$0.8031$^{**}$ & 0.0258 \\
 & & & ($-$2.68) & ($-$2.22) & & & ($-$2.68) & (0.28) \\
\midrule
Controls & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\
\midrule
Security FE & Yes & Yes & Yes & & Yes & Yes & Yes & \\
Fund FE & Yes & Yes & Yes & & Yes & Yes & Yes & \\
Time FE & Yes & Yes & Yes & & Yes & Yes & Yes & \\
Security $\times$ Time FE & & & & Yes & & & & Yes \\
Fund $\times$ Time FE & & & & Yes & & & & Yes \\
Fund $\times$ Security FE & & & & Yes & & & & Yes \\
\midrule
SE Clustering & Fund, Time & Fund, Time & Fund, Time & Fund, Time & Fund, Time & Fund, Time & Fund, Time & Fund, Time \\
Sample & Active & Active & Active & Active & Active & Active & Active & Passive \\
Adj.\ $R^2$ & 0.3288 & 0.3289 & 0.3291 & 0.8585 & 0.3289 & 0.3290 & 0.3292 & 0.8585 \\
$N$ & 42,512 & 42,512 & 42,512 & 39,109 & 42,512 & 42,512 & 42,512 & 11,288 \\
\bottomrule
\end{tabular}
}
\par\smallskip
{\footnotesize
\textit{Notes:} The table reports results from panel regressions of $PosChange_{i,j,t}$, the monthly percentage change in fund $j$'s position in stock $i$. The sample is restricted to observations within $\pm$3 months of a first-time public short position disclosure (the ``disclosure sample'') for stocks that were ever publicly disclosed as having a large net short position ($\mathit{ever\_LSP}=1$). $\mathit{OnLoan}_{i,j,t-1}$ is the dollar value of shares lent by fund $j$ in stock $i$ at month $t-1$ divided by the market capitalization of stock $i$, standardized to mean zero and unit standard deviation. $\mathit{Disclosure}_{i,t+1}$ equals one if stock $i$ has a \textit{new} mandatory public short position disclosure in month $t+1$, defined as a disclosure with no prior disclosure in the preceding six months. Columns~(1)--(7) are estimated for actively managed funds; column~(8) provides the passive fund placebo test. Columns~(1)--(3) and (5)--(7) include separate security, fund, and time fixed effects; columns~(4) and (8) include the full saturated fixed effects (security$\times$time, fund$\times$time, and fund$\times$security). Controls include lagged Amihud illiquidity rank and lagged position weight. Standard errors are double-clustered by fund and time. \textit{t}-statistics in parentheses. *, **, *** denote significance at the 10\%, 5\%, and 1\% levels.
}
